---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.com/UBESP-DCTV/select.svg?branch=master)](https://travis-ci.com/UBESP-DCTV/select)
[![Coverage status](https://codecov.io/gh/UBESP-DCTV/select/branch/master/graph/badge.svg)](https://codecov.io/github/UBESP-DCTV/select?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/select)](https://cran.r-project.org/package=select)

# select

The goal of select is to provide the code for the application of a
SuperLearner approach to predict run-in outcome in RCT.

## Installation

You can install the development version of the package `select` from
[GitHub](https://github.com/) with the following procedure:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/select")
```

## Contributor Code of Conduct
Please note that the `select` project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
